### 2018-02-02 Paper/jaccardbaetica.tex
introduction

%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

@@

All the amphora stamps belong to Dressel 20 types. Dressel 20 was used to transport olive oil along the province during the Roman Empire. There is evidence that stamps were used from three centuries. (economía oleica betica). Frequently, stamps were marked mostly in handles but rarely in rims and body.  
The information of the stamps is known as \textit{tria nomina} (HABLAR SOBRE EL DEBATE DE LOS INDIVIDUOS DE ACEITE O YO QUE SE). \textit{Tria Nomina} was mostly formed for a code of three letters.

The meaning of the amphora stamps is still under debate. Some authors suggest that they were identified as the owner of the olive land \citep{rodriguez_economioleicola_1977}. Other authors propose that stamp could be the owner of the amphorae workshop. In any case, the use of these stamps defined the system of working in the workshops. 
%habría que citar a Dressel

@@

>>>>

\bibliographystyle{model2-names.bst}\biboptions{authoryear}

@@

Material culture allows us to understand a part of mechanism of production... (aquí creo que me repito como siempre)

The economy of Roman Empire have been an object of study in the last centuries. (cambiar)

This paper aims to highlight the production dynamics in relation to a specific area within Roman Empire. We explore here the economic relation between stamps and workshops.

%this paper aims to highlight the production dynamic in connection with the proximity between amphora workshops and stamps.

All the amphora stamps belong to Dressel 20 types. Dressel 20 was used to transport olive oil along the province during the Roman Empire. There is evidence that stamps were used from three centuries. (economía oleica betica). Frequently, stamps were marked mostly in handles but rarely in rims and body.  
The information of the stamps is known as \textit{tria nomina} (HABLAR SOBRE EL DEBATE DE LOS INDIVIDUOS DE ACEITE O YO QUE SE). \textit{Tria Nomina} was mostly formed for a code three of letters. These letters can appear in a abbreviated form or complete \citep{berni_millet_amphora_1996}

The meaning of the amphora stamps is still under debate. Some authors suggest that they were identified as the owner of the olive land \citep{rodriguez_economioleicola_1977}. Other authors propose that stamp could be the owner of the amphorae workshop. In any case, the use of these stamps defined somehow the system of working in the workshops. 
%habría que citar a Dressel

@@

\section{References}
